Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-02-28 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
fix typos

Above, we thoroughly studied the relationship between the number of basis functions in the approximation and the approximation accuracy across different configurations. We specifically focused on the Matérn and squared exponential families of covariance functions, yet there exists other families of stationary covariance functions. The basis function approximation can easily be implemented for any stationary covariance function, where the spectral density function is available. The assess the accuracy of a basis function approximation for a kernel, where the diagnostic plots like Figure \ref{fig6_relationships} or equations (\ref{eq_m_l_QE})-(\ref{eq_c_vs_l_mat52}) are not available, we suggest to use the relative total variational distance between the true covariance function and the approximate covariance function as given in eq. \eqref{eq:rel_total_distance}. Ensuring that the relative distance is bounded by a small constant for the relevant lengthscale implies a high quality approximation. Other possibility to asses the accuracy of the approximation is to look at the cumulative sum of the spectral densities terms used in the series expansion and find out how much of the total variation are actually explaining.

>>>>

Above, we thoroughly studied the relationship between the number of basis functions in the approximation and the approximation accuracy across different configurations. We specifically focused on the Matérn and squared exponential families of covariance functions, yet there exists other families of stationary covariance functions. The basis function approximation can easily be implemented for any stationary covariance function, where the spectral density function is available. The assess the accuracy of a basis function approximation for a kernel, where the diagnostic plots like Figure \ref{fig6_relationships} or equations (\ref{eq_m_l_QE})-(\ref{eq_c_vs_l_mat52}) are not available, we suggest to use the relative total variational distance between the true covariance function and the approximate covariance function as given in eq. \eqref{eq:rel_total_distance}. Ensuring that the relative distance is bounded by a small constant for the relevant lengthscale implies a high quality approximation. Another possibility to asses the accuracy of the approximation is to look at the cumulative sum of the spectral densities terms used in the series expansion and find out how much of the total variation they are actually explaining.
